Abstract Binding Trees

### 2015-10-24 paper.tex
Use discrete for arities in pullback diagram
start talking a little bit about renaming (#10)
- [notation] Let 'a' range over arities rather than 'ρ'

Then, fix a covariant presheaf (copresheaf) of operators
$\Of{\Operators}{\SCtx\times\Discrete{\Arities}\to\Sets}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $C\Grothendieck{}{\Psi}$ represents the
  category of elements of a copresheaf $\Of{\Psi}{C\to\Sets}$ but we keep the
  $C$ implicit and simply refer to it as the Grothendieck construction.
  Alternatively, this construction can be understood as a coend
$\IMode{C\Grothendieck{}{\Psi}}\cong \IMode{\int^{c \in C}\Coslice{c}{C}
\otimes \Discrete{\Psi(c)}}$.} $\Of{\Grothendieck{}{(-)}}{\Sets^{C}\to\Cats}$
on operators we have a category of objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $\Of{f}{\Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}}$ such that
$\EqMember{\Restriction{f}\vartheta}{\vartheta'}{\Operators\Pair{\Upsilon'}{\varrho'}}$.
Equivalently, $\Grothendieck{}{\Operators}$ is the pullback of $\Operators$
along the universal $\Sets$-bundle where $\pi_{\Operators}$ is a discrete
Grothendieck opfibration and $\Forget{-}_{\Singleton}$ is the forgetful functor
from pointed sets:

\[
\begin{tikzcd}[ampersand replacement = \&, sep = large]
  {\Grothendieck{}{\Operators}}
    \arrow[r, "{\pi_{\in}}"]
    \arrow[d, "{\pi_{\Operators}}" left]
  \& {\Coslice{\Singleton}{\Sets}}
    \arrow[d, "{\Forget{-}_{\Singleton}}"] \\
  {\SCtx\times\Arities}
     \arrow[r, "{\Operators}" below]
  \& {\Sets} \\
\end{tikzcd}
\]

\[
  \infer{
    \IsOperator{\Upsilon}{\vartheta}{\varrho}
  }{
    \Member{\vartheta}{\Operators\langle\Upsilon,\varrho\rangle}
  }
\]

The judgment $\IsOperator{\Upsilon}{\vartheta}{\varrho}$ enjoys the structural
properties of weakening and exchange via the functoriality of
$\Operators$.

@@

Declaring a new assignable consists in providing an initial value, and an
expression with a free symbol (which shall represent the assignable in scope).
Weakening can be seen as inducing a ``degeneracy map'' on operators, whereas a
renaming $u\mapsto v$ will take $\mathsf{get}[u]$ to $\mathsf{get}[v]$.

>>>>

Then, fix a covariant presheaf (copresheaf) of operators
$\Of{\Operators}{\SCtx\times\Discrete{\Arities}\to\Sets}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $C\Grothendieck{}{\Psi}$ represents the
  category of elements of a copresheaf $\Of{\Psi}{C\to\Sets}$ but we keep the
  $C$ implicit and simply refer to it as the Grothendieck construction.
  Alternatively, this construction can be understood as a coend
$\IMode{C\Grothendieck{}{\Psi}}\cong \IMode{\int^{c \in C}\Coslice{c}{C}
\otimes \Discrete{\Psi(c)}}$.} $\Of{\Grothendieck{}{(-)}}{\Sets^{C}\to\Cats}$
on operators we have a category of objects
$\Member{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{a'}}{\vartheta'}}$
for $\Of{f}{\Pair{\Upsilon}{a}\to\Pair{\Upsilon'}{a'}}$ such that
$\EqMember{\Restriction{f}\vartheta}{\vartheta'}{\Operators\Pair{\Upsilon'}{a'}}$.
Equivalently, $\Grothendieck{}{\Operators}$ is the pullback of $\Operators$
along the universal $\Sets$-bundle where $\pi_{\Operators}$ is a discrete
Grothendieck opfibration and $\Forget{-}_{\Singleton}$ is the forgetful functor
from pointed sets:

\[
\begin{tikzcd}[ampersand replacement = \&, sep = large]
  {\Grothendieck{}{\Operators}}
    \arrow[r, "{\pi_{\in}}"]
    \arrow[d, "{\pi_{\Operators}}" left]
  \& {\Coslice{\Singleton}{\Sets}}
    \arrow[d, "{\Forget{-}_{\Singleton}}"] \\
  {\SCtx\times\Discrete{\Arities}}
     \arrow[r, "{\Operators}" below]
  \& {\Sets} \\
\end{tikzcd}
\]

\[
  \infer{
    \IsOperator{\Upsilon}{\vartheta}{a}
  }{
    \Member{\vartheta}{\Operators\langle\Upsilon,a\rangle}
  }
\]

The judgment $\IsOperator{\Upsilon}{\vartheta}{a}$ enjoys the structural
properties of weakening and exchange via the functoriality of
$\Operators$.

@@

Declaring a new assignable consists in providing an initial value, and an
expression with a free symbol (which shall represent the assignable in scope).
Note that the functoriality of $\Operators$ guarantees for any renaming
$\Of{\varrho}{\Upsilon\to\Upsilon'}$ a restriction map $\Restriction{\varrho}$
such that $\IsOperator{\Upsilon'}{\Restriction{\varrho}(\vartheta)}{a}$ when
$\IsOperator{\Upsilon}{\vartheta}{a}$. In particular, the renaming
$\Upsilon,u\mapsto\Upsilon,v$ shall take $\mathsf{get}[u]$ to
$\mathsf{get}[v]$.
